The Hot Hand Fallacy in Call of Duty Search and Destroy

### 2022-08-25 paper/paper.tex
longtable -> table, other small notation fixes

\title{The Hot Hand Fallacy in Call of Duty}

@@

6-0 sweeps make up 4.7\% of all series, while 6-5 series make up 23.7\%
of series. The observed offensive round win percentage across all rounds
is \(\tau_O\) = 47.8\%.\footnote{Offensive round win percentage has been
  nearly constant across the three games during the CDL era: 1. 47.2\%
  in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\% in Vanguard (2022)}
Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win
percentages by series ``state'' (i.e.~the number of round wins by each
team prior to an upcoming round). Offensive round win rate is not quite
constant, although never veers more than 10\% from \(\tau_O\).

\begin{longtable}{crrrrrr}
\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins. Numbers in parentheses are sample sizes.}\label{tbl:cod-o-win-prop-by-series-state} \\
\toprule
& \multicolumn{6}{c}{Offense round wins} \\ 
\cmidrule(lr){2-7}
Defense round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
\midrule
0 & 47.8\%
(852) & 46.6\%
(408) & 43.1\%
(216) & 43.5\%
(115) & 43.3\%
(67) & 40.5\%
(37) \\ 
1 & 48.6\%
(444) & 49.3\%
(418) & 51.5\%
(309) & 43.4\%
(205) & 43.3\%
(120) & 39.4\%
(99) \\ 
2 & 52.8\%
(218) & 48.9\%
(305) & 48.9\%
(315) & 46.6\%
(262) & 48.7\%
(189) & 42.1\%
(133) \\ 
3 & 54.5\%
(123) & 46.0\%
(200) & 49.6\%
(250) & 45.6\%
(248) & 44.4\%
(214) & 44.8\%
(174) \\ 
4 & 56.9\%
(65) & 54.5\%
(145) & 47.2\%
(193) & 44.7\%
(228) & 55.2\%
(221) & 50.5\%
(208) \\ 
5 & 47.4\%
(38) & 49.4\%
(83) & 47.1\%
(136) & 50.9\%
(175) & 45.2\%
(177) & 46.0\%
(202) \\ 
\bottomrule
\end{longtable}

@@

\begin{equation}\label{eq:chi-squ}
\chi^2 = \sum^{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)},
\end{equation}

@@

Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected
series lasting \(r\) rounds, the expected proportion of series given
\(\phi_0 = 0.5\), \(\hat{\Phi}_0(r)\), and the observed proportions,
\(\Phi(r)\).

\begin{longtable}{rrrr}
\caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$. Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
\toprule
$r$ & $N(r)$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ \\ 
\midrule
6 & 40 & $4.7\%$ & $3.1\%$ \\ 
7 & 101 & $11.9\%$ & $9.4\%$ \\ 
8 & 141 & $16.5\%$ & $16.4\%$ \\ 
9 & 185 & $21.7\%$ & $21.9\%$ \\ 
10 & 183 & $21.5\%$ & $24.6\%$ \\ 
11 & 202 & $23.7\%$ & $24.6\%$ \\ 
\bottomrule
\end{longtable}

@@

\begin{longtable}{lrr}
\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}\label{tbl:mosteller-methods-results} \\
\toprule
Method & $\phi$ & $\chi^2$ ($p$-value) \\
\midrule
0. Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
1. Method of moments & 0.5725 & 3.6 (0.6) \\
2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\
\bottomrule
\end{longtable}

Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new
\(\hat{\Phi}(r)\) when re-applying Equation \ref{eq:series-length} for
the maximum likelihood estimate \(\phi_2 = 0.575\), resulting in a new
set of expected proportions of series lasting \(r\) rounds
\(\hat{\Phi}_2(r)\).\footnote{The method of moments and minimum
  \(\chi^2\) estimates for \(\phi\) are omitted simply because the
  results would be nearly identical to those for the maximum likelihood
  estimate of \(\phi\) (since they are all \(\approx 0.575\)).} We
observe that \(\hat{\Phi}_2(r)\) is larger than \(\hat{\Phi}_0(r)\) for
\(r \in [6, 7]\), more closely matching \(\Phi(r)\). \(\hat{\Phi}_2(r)\)
is also closer to the observed \(\Phi(r)\) for \(r \in [9, 10]\),
although not for \(r \in [8, 11]\).

\begin{longtable}{rrrr}
\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
\toprule()
$r$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 \\
\midrule()
\endhead
6 & 4.7\% & 3.1\% & 4.2\% \\
7 & 11.9\% & 9.4\% & 11.2\% \\
8 & 16.5\% & 16.4\% & 17.8\% \\
9 & 21.7\% & 21.9\% & 21.8\% \\
10 & 21.5\% & 24.6\% & 23.0\% \\
11 & 23.7\% & 24.6\% & 22.0\% \\
\bottomrule()
\end{longtable}

@@

Given that people typically perceive streaks as beginning after the
third success (or failure) at minimum (Carlson and Shu 2007), we focus
on streaks of three round wins.\footnote{Three happens to also be a
  reasonable number for series that last at maximum 11 rounds.} Table
\ref{tbl:cod-pw3r-pl3r} compares the notional and MS expected
proportions, \(\hat{P}^{+|k,r}_0\) and \(\hat{P}^{+|k,r}_{MS}\)
respectively, with the observed round win rate, \(P^{+|kr}\), following
streaks of \(k=3\) round wins given the series outcome.

\begin{longtable}{rcrrrrr}
\caption{Given the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ instances where a team could win after the streak ($P^{+|k=3,r} = \frac{r^{+|k=3,r}}{N^{k=3,r}}$). Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ respectively.}
\label{tbl:cod-pw3r-pl3r} \\

\toprule
$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ & $\hat{P}^{+|k=3,r}_0$ & $\hat{P}^{+|=k=3,r}_{MS}$ \\ 
\midrule

@@

\bottomrule
\end{longtable}

@@

Now let us explicitly consider the round, \(i\). As shown in Table
\ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round \(i\)
immediately following a streak of \(k\) round wins in a series lasting
\(r\) rounds, \(\hat{P}{+|k,r,i}_0\), is statistically different than
the observed \(P^{+|k,r,i}\) in several cases, notably when \(r = i\)
for each of \(r \in [9, 10, 11]\).\footnote{The null can also be
  rejected for \(r \in [7, 8]\), although these are not shown, and the
  sample sizes are smaller.} Interestingly, the observed rate is greater
than the expected rate in each case where we can reject the null
hypothesis, whereas the observed rate is less than the expected rate in
all other cases, as well in a strong majority of cases not shown.

\begin{longtable}{rrcrrrr}
\caption{Given the round win streak $k=3$, the index of the round immediately following the streak $i$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak. Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$. Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$ for brevity.}
\label{tbl:cod-pw3ri-pl3ri} \\
\toprule
$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ & $\hat{P}^{+|k=3,r,i}_0$\\ 
\midrule

@@

\bottomrule
\end{longtable}

@@

In Table \ref{tbl:cod-runs}, the observed and expected count of
sequences, \(N^{\zeta r}\) and \(\hat{N}^{\zeta r}\) respectively, are
shown for sequences, \(\zeta(r)\), for which one can reject the
Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial
success \(\phi = 0.575\),\footnote{If we used \(\phi = 0.5\), we would
  get the same exact seqeunces.} at a confidence level of
\(\alpha = 0.05\), for \(r \in [8, 9, 10]\). In addition to the 13
sequences shown, there are 12 additional sequences for \(r = 11\).

\begin{longtable}{rlrrrr}

\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively. The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$. $\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
\label{tbl:cod-runs} \\

\toprule
r & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
\midrule
8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\ 
\bottomrule
\end{longtable}

>>>>

\title{The Hot Hand Fallacy in Call of Duty Search and Destroy}

@@

6-0 sweeps make up 4.7\% of all series, while 6-5 series make up 23.7\%
of series. The observed offensive round win percentage across all rounds
is \(\tau_O\) = 47.8\%.\footnote{Offensive round win percentage has been
  nearly constant across the three games during the CDL era: 1. 47.2\%
  in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\% in Vanguard (2022)}
Table \ref{tbl:o-win-prop-by-series-state} shows round win percentages
by series ``state'' (i.e.~the number of round wins by each team prior to
an upcoming round). Offensive round win rate is not quite constant,
although never veers more than 10\% from \(\tau_O\).

\begin{table}

\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins. Numbers in parentheses are sample sizes.}

\centering
\begin{tabular}{crrrrrr}
\toprule
& \multicolumn{6}{c}{Offense round wins} \\ 
\cmidrule(lr){2-7}
Defense round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
\midrule

0 & 47.8\%(852) & 46.6\%(408) & 43.1\%(216) & 43.5\%(115) & 43.3\%(67)  & 40.5\%(37)  \\
1 & 48.6\%(444) & 49.3\%(418) & 51.5\%(309) & 43.4\%(205) & 43.3\%(120) & 39.4\%(99)  \\
2 & 52.8\%(218) & 48.9\%(305) & 48.9\%(315) & 46.6\%(262) & 48.7\%(189) & 42.1\%(133) \\
3 & 54.5\%(123) & 46.0\%(200) & 49.6\%(250) & 45.6\%(248) & 44.4\%(214) & 44.8\%(174) \\
4 & 56.9\%(65)  & 54.5\%(145) & 47.2\%(193) & 44.7\%(228) & 55.2\%(221) & 50.5\%(208) \\
5 & 47.4\%(38)  & 49.4\%(83)  & 47.1\%(136) & 50.9\%(175) & 45.2\%(177) & 46.0\%(202) \\

\bottomrule
\end{tabular}

\label{tbl:o-win-prop-by-series-state}

\end{table}

@@

\begin{equation}\label{eq:chi-squ}
\chi^2 = \sum_{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)},
\end{equation}

@@

Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected series
lasting \(r\) rounds, the expected proportion of series given
\(\phi_0 = 0.5\), \(\hat{\Phi}_0(r)\), and the observed proportions,
\(\Phi(r)\).

\begin{table}
\caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$. Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}

\centering
\begin{tabular}{rrrr}
\toprule
$r$ & $N(r)$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ \\ 
\midrule

6 & 40 & $4.7\%$ & $3.1\%$ \\ 
7 & 101 & $11.9\%$ & $9.4\%$ \\ 
8 & 141 & $16.5\%$ & $16.4\%$ \\ 
9 & 185 & $21.7\%$ & $21.9\%$ \\ 
10 & 183 & $21.5\%$ & $24.6\%$ \\ 
11 & 202 & $23.7\%$ & $24.6\%$ \\

\bottomrule
\end{tabular}

\label{tbl:prob-series-lasts-r-rounds}

\end{table}

@@

\begin{table}

\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}

\centering
\begin{tabular}{lrr}
\toprule
Method & $\phi$ & $\chi^2$ ($p$-value) \\
\midrule

0. Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
1. Method of moments & 0.5725 & 3.6 (0.6) \\
2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\

\bottomrule
\end{tabular}

\label{tbl:mosteller-methods-results}

\end{table}

Table \ref{tbl:alternative-constant-ps} shows the new \(\hat{\Phi}(r)\)
when re-applying Equation \ref{eq:series-length} for the maximum
likelihood estimate \(\phi_2 = 0.575\), resulting in a new set of
expected proportions of series lasting \(r\) rounds
\(\hat{\Phi}_2(r)\).\footnote{The method of moments and minimum
  \(\chi^2\) estimates for \(\phi\) are omitted simply because the
  results would be nearly identical to those for the maximum likelihood
  estimate of \(\phi\) (since they are all \(\approx 0.575\)).} We
observe that \(\hat{\Phi}_2(r)\) is larger than \(\hat{\Phi}_0(r)\) for
\(r \in [6, 7]\), more closely matching \(\Phi(r)\). \(\hat{\Phi}_2(r)\)
is also closer to the observed \(\Phi(r)\) for \(r \in [9, 10]\),
although not for \(r \in [8, 11]\).

\begin{table}
\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}

\centering
\begin{tabular}{rrrrrr}
\toprule
$r$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 \\
\midrule

6 & 4.7\% & 3.1\% & 4.2\% \\
7 & 11.9\% & 9.4\% & 11.2\% \\
8 & 16.5\% & 16.4\% & 17.8\% \\
9 & 21.7\% & 21.9\% & 21.8\% \\
10 & 21.5\% & 24.6\% & 23.0\% \\
11 & 23.7\% & 24.6\% & 22.0\% \\

\bottomrule
\end{tabular}

\label{tbl:alternative-constant-ps}

\end{table}

@@

Given that people typically perceive streaks as beginning after the
third success (or failure) at minimum (Carlson and Shu 2007), we focus
on streaks of three round wins.\footnote{Three happens to also be a
  reasonable number for series that last at maximum 11 rounds.} Table
\ref{tbl:pwkr} compares the notional and MS expected proportions,
\(\hat{P}^{+|k,r}_0\) and \(\hat{P}^{+|k,r}_{MS}\) respectively, with
the observed round win rate, \(P^{+|kr}\), following streaks of \(k=3\)
round wins given the series outcome.

\begin{table}

\caption{Given the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ instances where a team could win after the streak ($P^{+|k=3,r} = \frac{r^{+|k=3,r}}{N^{k=3,r}}$). Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ respectively.}

\centering
\begin{tabular}{rcrrrrr}
\toprule
$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ & $\hat{P}^{+|k=3,r}_0$ & $\hat{P}^{+|=k=3,r}_{MS}$ \\ 
\midrule

@@

\bottomrule
\end{tabular}

\label{tbl:pwkr}

\end{table}

@@

Now let us explicitly consider the round, \(i\). As shown in Table
\ref{tbl:pw3ri}, the notional win rate in the round \(i\) immediately
following a streak of \(k\) round wins in a series lasting \(r\) rounds,
\(\hat{P}{+|k,r,i}_0\), is statistically different than the observed
\(P^{+|k,r,i}\) in several cases, notably when \(r = i\) for each of
\(r \in [9, 10, 11]\).\footnote{The null can also be rejected for
  \(r \in [7, 8]\), although these are not shown, and the sample sizes
  are smaller.} Interestingly, the observed rate is greater than the
expected rate in each case where we can reject the null hypothesis,
whereas the observed rate is less than the expected rate in all other
cases, as well in a strong majority of cases not shown.

\begin{table}

\caption{Given the round win streak $k=3$, the index of the round immediately following the streak $i$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak. Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$. Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$ for brevity.}

\centering
\begin{tabular}{rrcrrrr}
\toprule
$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ & $\hat{P}^{+|k=3,r,i}_0$\\ 
\midrule

@@

\bottomrule
\end{tabular}

\label{tbl:pw3ri}

\end{table}

@@

In Table \ref{tbl:ww-sequences}, the observed and expected count of
sequences, \(N^{\zeta r}\) and \(\hat{N}^{\zeta r}\) respectively, are
shown for sequences, \(\zeta(r)\), for which one can reject the
Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial
success \(\phi = 0.575\),\footnote{If we used \(\phi = 0.5\), we would
  get the same exact seqeunces.} at a confidence level of
\(\alpha = 0.05\), for \(r \in [8, 9, 10]\). In addition to the 13
sequences shown, there are 12 additional sequences for \(r = 11\).

\begin{table}

\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively. The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$. $\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}

\centering
\begin{tabular}{rlrrrr}
\toprule
$r$ & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
\midrule
8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\

\bottomrule
\end{tabular}

\label{tbl:ww-sequences}
\end{table}
